%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
\documentclass{cv}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = blue, anchorcolor = blue]{hyperref}

\begin{document}
\contact{Mike Vink}
{Utrecht}
{+31 6 40970634}
{mike1994vinkm@gmail.com}
{www.vinkland.xyz}

\section{Summary}
\section{Experience}

\experience
{November 2019}{November 2020}
{Research Intern at the Structural Neurobiology group of Dr. ir. Bert Janssen}
{Utrecht University}{
\item Researched the structure of a neuronal protein using crystallisation and X-ray diffraction. Designed primers and purified protein constructs. Performed biophysical tests to research protein protein interactions for constructs (mostly SEC, SEC-MALS, AUC). Designed and set up crystallisation trials for constructs. Fished for crystals and prepared samples for synchotron. Wrote a thesis giving a literature review and summarising results.
}

\experience
{Februari 2018}{May 2018}
{Research Intern at the X-Ray and Crystallography group of Dr. Piet Gros}
{Utrecht University}{
\item
}

\section{Skills}
\section{Education}

\experience
{September 2019}{May 2021}
{Molecular and Cellular Life Sciences, MSc.}
{Utrecht University}{
\item Enrolled in the biophysics and molecular imaging major and got a 7.8/10 grade average over the entire masters. Completed crystallography and molecular dynamics courses. Wrote an article reviewing different protein cavity detection algorithms.
\item Enrolled in the applied datascience minor and got a 8.6/10 grade over the projects and courses in the minor. Completed courses about programming machine learning algorithms "deep learning" and "data mining". Applied machine learning algorithms in research projects "Comparative study of state-of-the-art GANs" and "a data exploration using the FluPrint database".
}

\experience
{September 2014}{May 2018}
{Molecular Life Sciences, BSc.}
{Utrecht University}{
\item Enrolled in courses related to molecular imaging techniques (crystallography, NMR, and molecular dynamics). Part of multiple student organisations, biology and chemistry student groups, utrecht student rugby society (USRS) for 1 year, and student rowing club ORCA for 1 year. Made final round for high level rowing competition try outs.
}

\section{Certifications}
\end{document}
